Exploring the Utility of Machine Learning Across Varied Data Formats

### 2024-05-26 homework2/paper/paper.tex
MLP from scikit

\subsection{Multi-Layered Perceptron (MLP)}
Multi-Layer Perceptron (MLP) is a type of artificial neural network designed to 
capture complex, non-linear patterns in data. Unlike Linear Regression, which is
limited to linear relationships, MLPs consist of multiple layers of interconnected 
nodes, or neurons, that can model intricate interactions between variables.

MLPs are particularly suitable for tasks involving complex datasets with 
non-linear relationships, such as salary prediction. In salary prediction, 
factors like education, work experience, industry sector, and other 
socio-economic variables interact in complex ways that Linear Regression might 
not fully capture. MLPs can learn these non-linear patterns, providing a more 
accurate and nuanced understanding of the factors influencing salary levels.

>>>>

\subsection{Multi-Layered Perceptron (MLP)}
A Multilayer Perceptron (MLP) is a class of feedforward artificial neural network 
that consists of at least three layers of nodes: an input layer, one or more 
hidden layers, and an output layer. Each node, except for the input nodes, is a 
neuron that uses a nonlinear activation function. MLPs are capable of modeling 
complex relationships in data, making them suitable for tasks such as 
classification, regression, and pattern recognition. The network learns by 
adjusting the weights through a process called backpropagation, which minimizes 
the error between the predicted outputs and the actual targets. This 
adaptability and learning capability make MLPs powerful tools in machine 
learning and artificial intelligence applications.

In the \textit{mlp} folder at the root of the project directory, we implemented the
Multi-Layered Perceptron algorithm in two different ways:

\begin{itemize}
    \item \textit{MLP with Scikit-Learn:} We used the Scikit-Learn library to implement
    the MLP algorithm on the preprocessed datasets.
    \item \textit{MLP from Scratch:} We implemented the MLP algorithm from scratch using
    the Negative Log-Likelihood method, the Gradient Descent optimization algorithm, and
    the Sigmoid activation function.
\end{itemize}

Before starting the implementation of the MLP algorithm, we need to standardize the
numeric attributes in the datasets as in the Logistic Regression algorithm.

For the MLP with Scikit-Learn implementation, we used the \textit{MLPClassifier} class
from the \textit{sklearn.neural\_network} module to train the model on the preprocessed
datasets, without setting any hyperparameters, using the default values.

For the MLP from Scratch implementation, we implemented the Negative Log-Likelihood loss
function, the Gradient Descent optimization algorithm, and the Sigmoid activation function.
We trained the model on the preprocessed datasets, setting the learning rate to 0.01, the
number of epochs to 10000, and the number of hidden units to 100. For the regularization,
we used the Ridge Regression technique.

The results of both implementations for each dataset are saved in the \textit{MLP}
folder at the specific dataset's root.
